IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-07 paper/formal.tex
minor fixes from reviewer 2

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Fig.~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS2 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce
(in two steps)
to |ic1 = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straightforward, see Section~\ref{sec:extensions}.}
then the |sec| task's decision to diverge or not is directly leaked to a
public entity.

>>>>

However, even non-adversarial schedulers are not always safe.
Consider, for example, the sequential scheduling policy |seqf| given in
Fig.~\ref{fig:scheduler}.
%
It is easy to show that |specLang seqf targetLang| does not satisfy
TSNI:
%
consider a target language similar to |targetLangML| with an
additional expression terminal |diverge| that denotes a divergent computation,
i.e., |diverge| always reduces to |diverge| and a simple label lattice |{pub,
sec}| such that |canFlowTo2 pub sec|, but |cantFlowTo2 sec pub|.
Consider the following two configurations in this language:
\begin{code}
ic1 = iS ; fullconf 1 sec tS1 (IT(if false then diverge else true)),  fullconf 2 pub tS2 ie
ic2 = iS ; fullconf 1 sec tS1 (IT(if true then diverge else true)),   fullconf 2 pub tS2 ie
\end{code}
These two configurations are |pub|-equivalent, but |ic1| will reduce
(in two steps)
to |ic1' = iS ; fullconf 2 pub tS1 (IT true)|, whereas |ic2| will not make
any progress.
%
Suppose that |ie| is a computation that writes to a |pub| channel,\footnote{
Though we do not model labeled channels, extending the calculus with such a
feature is straightforward, see Section~\ref{sec:extensions}.}
then the |sec| task's decision to diverge or not is directly leaked to a
public entity.

### 2015-01-07 paper/retrofit.tex
minor errors from reviewer 1
minor fixes from reviewer 2

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be above the task's current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
$|recvf ix1 ix2 ie1 ie2|$
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise, if there are no messages, that task continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il ((il', id, ie) , Q )| = \left\{
\begin{array}{l l}
|(il', id, ie) , filter il Q| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.

>>>>

These asynchronous communication primitives are worth further
discussion.  When a task is sending a message using |send|, it also labels that
message with a label |il'| (which must be at or above the task's current label |il|).
Messages can only be received by a task if its current label is
at least as high as the label of the message.
Specifically, receiving a message using
$|recvf ix1 ix2 ie1 ie2|$
binds the message and the sender's task identifier
to local variables |ix1| and |ix2|, respectively, and then executes |ie1|.
Otherwise, if there are no messages, that task continues its execution with |ie2|.
We denote the filtering of the message queue by |filter il Q|,
which is defined as follows.
If |Q| is the empty list |nil|, the
function is simply the identity function, i.e.,
|filter il nil = nil|, and otherwise:
\[
|filter il (((il', id, ie) , Q) )| = \left\{
\begin{array}{l l}
|(il', id, ie) , (filter il Q)| & \quad \text{if |il' canFlowTo il|}\\
|filter il Q| & \quad \text{otherwise}
\end{array} \right.
\]
This ensures that tasks cannot receive messages that are more sensitive
than their current label would allow.
